Capon Beamforming Applied on Moving Objects - An Analysis of Local Lateral Shift-Invariance

### 2013-12-17 HRUIofMovingObjects/jrnl_article.tex
Moving objects: writing, updated figures

\subsection{Oversampling on Transmit}
A straight forward way of obtaining sufficient sampling in an active imaging system is by increasing the number of transmit beams (tx-beams) until the system is locally laterally shift-invariant. In Fig.\,\ref{fig:capon_oversampling_a} and Fig.\,\ref{fig:capon_oversampling_b} we have increased the lateral sampling on transmit by a $q$-factor of four and ten respectively. As expected the geometric distortion and scalloping loss decreases with increased lateral sampling. Note that Fig.\,\ref{fig:capon_oversampling_b} is zoomed compared to Fig.\,\ref{fig:capon} in order to better see the beam-to-beam variation.

From Fig.\,\ref{fig:capon_oversampling_b} we see that more than ten times oversampling has to be applied to achieve a local lateral shift-invariant Capon beamformer when a moving point scatterer is imaged without noise and with the same parameters as in Fig\,\ref{fig:capon}. %$1/100$ in diagonal loading. 
Note again that a diagonal loading factor of $1/100$ will introduce a white noise component in the sample covariance matrix $20$ dB lower than the signal present. Hence, the covariance has been estimated from data which appeared to have an SNR of 20 dB.

@@

\begin{figure*}[!t]
\centerline{
\subfloat[]{
\includegraphics[width=0.5\linewidth]{\img fig4a.eps}\label{fig:capon_oversampling_a}
}
\subfloat[]{
\includegraphics[width=0.5\linewidth]{\img fig4b.eps}\label{fig:capon_oversampling_b}
}
}
\caption{Capon beamforming as described in Fig\,\ref{fig:capon} with oversampling on transmit. The figure is zoomed compared with Fig\,\ref{fig:capon} to better see the beam-to-beam variation. a) Four times oversampling. b) Ten times oversampling. The maximum scalloping loss is still too high for the system to be called locally laterally shift invariant.}
\label{fig:capon_oversampling}
\end{figure*}

@@

In cardiac ultrasound imaging, PRB is typically used in order to keep the number of rx-beams high while the number of tx-beams are reduced. When using PRB for oversampling we would like to maintain the same number of tx-beams while the number of rx-beams are increased. The acquisition frame rate will then not be affected. On the other hand more rx-beams will increase the number of covariance matrices, and thereby the number of matrix-inversions with a factor equal to the number of parallel receive lines. The processing times reported in \cite{Asen} will then also increase with the same factor. Since more than ten times oversampling is required in order to achieve lateral shift invariant high resolution imaging of a moving point scatterer, none of the implementations described in \cite{Asen} would be real time any more. We therefore need a different way of oversampling our imaging sector.

@@

\begin{figure*}[!t]
	\centerline{
		\subfloat[]{
			\includegraphics[width=0.5\linewidth]{\img fig5a.eps}
		}
		\subfloat[]{
			\includegraphics[width=0.5\linewidth]{\img fig5b.eps}
		}
	}
	\caption{Capon beamforming as described in Fig\,\ref{fig:capon} with oversampling based on phase rotation. The figure is zoomed compared with Fig\,\ref{fig:capon} to better see the beam-to-beam variation. a) 4x oversampling. b) 10x oversampling.}
	\label{fig:benchmark_capon_bs}
\end{figure*}

@@

Figure \ref{fig:phantom_capon_LSV_10PR} presents the result of applying ten times oversampling by phase rotation. We observe how the amplitude of the point scatterer is better preserved in all frames, and the scalloping loss is not far from our 1 dB threshold. Note that the oscillation along the diagonal does not indicate shift-variance. It is a result of lack of control when the probe was manually dragged across the phantom. In order to get a diagonal without peaks the probe has to be dragged across the phantom with a speed which matches the acquisition frame rate. In addition, due to the increase in lateral resolution, the Capon beamformer requires smaller frame-to-frame movements than DAS. Looking at the video of Capon beamforming with ten times oversampling by phase rotation \multimedia{Video Capon + 10PR} the blinking is now highly reduced. %The system is however not fully shift invariant. To achieve this a higher level of oversampling, %We therefore conclude that the system is now locally laterally shift invariant.

>>>>

\subsection{Oversampling on Transmit}
A straight forward way of obtaining sufficient sampling in an active imaging system is by increasing the number of transmit beams (tx-beams) until the system is locally laterally shift-invariant. In Fig.\,\ref{fig:capon_oversampling_a} and Fig.\,\ref{fig:capon_oversampling_b} we have increased the lateral sampling on transmit by a $q$-factor of four and sixteen respectively. As expected the geometric distortion and scalloping loss decreases with increased lateral sampling. Note that Fig.\,\ref{fig:capon_oversampling_b} is zoomed compared to Fig.\,\ref{fig:capon} in order to better see the beam-to-beam variation.

From Fig.\,\ref{fig:capon_oversampling_b} we see that sixteen times oversampling is not enough to achieve a local lateral shift-invariant Capon beamformer when a moving point scatterer is imaged without noise and with the same parameters as in Fig\,\ref{fig:capon}, but we are getting closer. %$1/100$ in diagonal loading. 
Note again that a diagonal loading factor of $1/100$ will introduce a white noise component in the sample covariance matrix $20$ dB lower than the signal present. Hence, the covariance has been estimated from data which appeared to have an SNR of 20 dB.

@@

\begin{figure*}[!t]
\centerline{
\subfloat[]{
\includegraphics[width=0.5\linewidth]{\img fig4a.eps}\label{fig:capon_oversampling_a}
}
\subfloat[]{
\includegraphics[width=0.5\linewidth]{\img fig4b.eps}\label{fig:capon_oversampling_b}
}
}
\caption{Capon beamforming as described in Fig\,\ref{fig:capon} with oversampling on transmit. The figure is zoomed compared with Fig\,\ref{fig:capon} to better see the beam-to-beam variation. a) Four times oversampling. b) Sixteen times oversampling. Even though its reduced, the maximum scalloping loss is still too high for the system to be named locally laterally shift invariant.}
\label{fig:capon_oversampling}
\end{figure*}

@@

In cardiac ultrasound imaging, PRB is typically used in order to keep the number of rx-beams high while the number of tx-beams are reduced. When using PRB for oversampling we would like to maintain the same number of tx-beams while the number of rx-beams are increased. The acquisition frame rate will then not be affected. On the other hand more rx-beams will increase the number of covariance matrices, and thereby the number of matrix-inversions with a factor equal to the number of parallel receive lines. The processing times reported in \cite{Asen} will then also increase with the same factor. Since more than ten times oversampling is required in order to achieve lateral shift invariant high resolution imaging of a moving point scatterer \textit{in-vitro}, none of the implementations described in \cite{Asen} would be real time any more. We therefore need a different way of oversampling our imaging sector.

@@

\begin{figure*}[!t]
	\centerline{
		\subfloat[]{
			\includegraphics[width=0.5\linewidth]{\img fig5a.eps}
		}
		\subfloat[]{
			\includegraphics[width=0.5\linewidth]{\img fig5b.eps}
		}
	}
	\caption{Capon beamforming as described in Fig\,\ref{fig:capon} with oversampling based on phase rotation. The figure is zoomed compared with Fig\,\ref{fig:capon} to better see the beam-to-beam variation. a) Four times oversampling. b) Sixteen times oversampling.}
	\label{fig:benchmark_capon_bs}
\end{figure*}

@@

Figure \ref{fig:phantom_capon_LSV_10PR} presents the result of applying sixteen times oversampling by phase rotation. We observe how the amplitude of the point scatterer is better preserved in all frames, and the scalloping loss is not far from our 1 dB threshold. Note that the oscillation along the diagonal does not indicate shift-variance. It is a result of lack of control when the probe was manually dragged across the phantom. In order to get a diagonal without peaks the probe has to be dragged across the phantom with a speed which matches the acquisition frame rate. In addition, due to the increase in lateral resolution, the Capon beamformer requires smaller frame-to-frame movements than DAS. Looking at the video of Capon beamforming with ten times oversampling by phase rotation \multimedia{Video Capon + 10PR} the blinking is now highly reduced. %The system is however not fully shift invariant. To achieve this a higher level of oversampling, %We therefore conclude that the system is now locally laterally shift invariant.
